On the Dynamics of Anthropomorphism in Robotics

### 2013-05-23 anthropomorphism.tex
Explain the 'normalized level' on the model diagram

>>>>

The model uses a \emph{normalized} level of anthropomorphic effects: because
anthropomorphic effects are not quantified on an absolute scale, we present
them as a normalized value, that span from a minimum (no anthropomorphic
effects) to a maximum (corresponding to the novelty effect peak on
Figure~\ref{fig:dynamics}). The actual maximum value of anthropomorphic effects
is strongly correlated to the human, the robot and other factors we introduce
below. Hence, the model we propose only focuses on the general \emph{shape} of
the level of antropomorphism over time, \ie the general dynamics of
anthropomorphism.
